Working title: Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-10-06 write_up/mixfishsim_ecolmod.tex
Added new plot

The factor most contributing to differences in fishing mortality before and
after the closure was the population (72 \% showing that the closures were
effective for population 3), followed by data resolution (21 \%), data type (7
\%) with the least important factor the timescale ($<$ 1 \%). In general the
finer the spatial resolution of the data used the greater reduction in fishing
mortality for population 3 after the closures (Figure \ref{fig:4}). The notable
outliers are the commercial data at the coarsest spatial resolution (20 x 20)
at a yearly and weekly timescale, where closures were nearly as effective as
the fine-scale resolution. In this case the closures were sufficiently large to
protect a core area of the habitat for the population, but this was achieved in
a fairly crude manner by closing a large area - including area where the
species was not found (Figure \ref{fig:17}) that may have consequences in terms
of restricting the fishery in a much larger area than necessary. \\

@@

The yearly data assumes the same proportion of each population caught at any
time of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The monthly data shows some consistency between the real
population and commercial data for population 2 - 4, though population 1 remains
under-represented.  On an annual basis, interestingly the commercial data under
represents the first species (in red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where population 1 are present and the survey sampling
areas where population 1 is more abundant than on average. This indicates that
fixed closures, at the right resolution, when based on commercially derived
data have the potential to reduced fishing mortality. The likely cost of poor
spatial and temporal resolution is associated with reduced effectiveness and
potentially closing fishing opportunities for other fisheries. \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
		box in relation to a) before the closure fishing locations, b)
		after the closure fishing locations, c) population 3 habitat
		distribution.}
	\label{fig:17}
\end{figure}	
%\end{comment}

>>>>

The factor most contributing to differences in fishing mortality before and
after the closure was the population (72 \% showing that the closures were
effective for population 3), followed by data resolution (21 \%), data type (7
\%) with the least important factor the timescale ($<$ 1 \%). In general the
finer the spatial resolution of the data used the greater reduction in fishing
mortality for population 3 after the closures (Figure \ref{fig:4}). The notable
outliers are the commercial data at the coarsest spatial resolution (20 x 20)
at a yearly and weekly timescale, where closures were nearly as effective as
the fine-scale resolution. In this case the closures were sufficiently large to
protect a core area of the habitat for the population, but this was achieved in
a fairly crude manner by closing a large area - including area where the
species was not found (Figure \ref{fig:17}) that may have consequences in terms
of restricting the fishery in a much larger area than necessary. We found that
these trade-offs existed, with high catches maintained with an effective
closure when the highest resolution data was used, with the effect being linear
when the true population distribution was known and also persisting for
closures based on commercial information (Figure \ref{fig:ce}).\\

@@

The yearly data assumes the same proportion of each population caught at any
time of the year due to the data aggregation. This assumption introduces
`aggregation bias' as the data may only be representative of some point (or no
point) in time. The monthly data shows some consistency between the real
population and commercial data for population 2 - 4, though population 1 remains
under-represented.  On an annual basis, interestingly the commercial data under
represents the first species (in red) while the survey over represents species
1. This is likely due to the biases in commercial sampling, with the fisheries
not targeting the areas where population 1 are present and the survey sampling
areas where population 1 is more abundant than on average. This indicates that
fixed closures, at the right resolution, when based on commercially derived
data have the potential to reduced fishing mortality. The likely cost of poor
spatial and temporal resolution is associated with reduced effectiveness and
potentially closing fishing opportunities for other fisheries (Figure
\ref{fig:ce}). \\

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{Closure fishing locations based on annual closures with a
		coarse spatial resolution. Closure location can be seen in red
		box in relation to a) before the closure fishing locations, b)
		after the closure fishing locations, c) population 3 habitat
		distribution.}
	\label{fig:17}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[width =\linewidth]{./Plots/Closure_effectiveness_CF}
	\caption{Effectiveness of closure with regards to reducing fishing
		mortality on protected population (further left on x-axis is
		best) and maintaining high catches in the fishery (highest on
		y-axis is best). The grey line indicates the direction of the
		trade-off between reducing fishing mortality and overall
		catches.}
	\label{fig:ce}
\end{figure}

%\end{comment}
